---
# General Settings
format: html
echo: false
warning: false

# Theme Settings
theme: 
  - flatly
brand:
  # logo: images/nefmc_logo.png
  color:    
    palette:
      dark-navy: "#104149"
      dark-blue: "#1d365e"
      teal: "#3e9eb6"
      light-blue: "#92b3e4"
      orange: "#ef953d"
      gray: "#7f7f7f"
    # background: light-blue
    foreground: dark-navy
    primary: dark-blue
    secondary: teal
    tertiary: gray
    warning: orange
  typography:
    base: 
      family: Urbanist
    headings: 
      family: Source Serif 4
    link: 
      color: teal
barcolor: "#3e9eb6"
barposition: top
footer-left: "Made with [surveydown](https://surveydown.org)"
footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/surveydown-dev/template_default)'

# Survey Settings
survey-settings:
  show-previous: true
  use-cookies: false
  auto-scroll: false
  rate-survey: false
  system-language: en
  highlight-unanswered: true
  highlight-color: blue
  capture-metadata: true
  all-questions-required: false
  required-questions:
    - report_year
    - stock
    - overfished
    - overfishing
    - recruit_incl
    - assessment_type
    - retro_pattern
    - climate_vulnerability
    - climate_direction
    - other_fish_quota
    - signif_catch_present

system-messages:
  previous: Previous
  next: Next
---

```{r}
library(surveydown)
library(tidyverse)
```

::: {.sd_page id=welcome}

<!-- --- page_1 -->

# Risk Policy Matrix

This is a survey for generating risk policy matrices and should be completed by tech staff. It has four pages for each group theme.

```{r report year}
sd_question(
  type = "textarea",
  id = "report_year", 
  label = "Reporting year", 
  height = "50px",
  placeholder = as.character(lubridate::year(lubridate::now()))
)
```

```{r stock}
sd_question("stock")
```

### Stock Status and Uncertainty Questions
Using the most recent stock assessment report for your stock, answer the following questions:

#### Biomass Stock Status

```{r overfished}
sd_question("overfished")
```

```{r overfishing}
sd_question("overfishing")
```

```{r rebuilding}
# sd_question("rebuilding_plan")
sd_question(
  type = "mc",
  id = "rebuilding_plan", 
  label = "Is this stock in a rebuilding plan?",
  options = c(
    "Yes" = "rebuilding_plan",
    "No" = "no_rebuilding"
    )
)
```

```{r rebuilding_target}
sd_question(
  type = "textarea",
  id = "rebuilding_target",
  label = "What is the rebuilding target?",
  height = "50px",
  placeholder = "Enter a year"
  )
```

```{r ssb target}
sd_question(
  type = "textarea",
  id = "ssb",
  label = "What is the terminal year estimate of SSB in metric tons?",
  height = "50px",
  placeholder = "Enter a year")

sd_question(
  type = "textarea",
  id = "relative_ssb",
  label = "What is the percentage of estimated SSB relative to the target SSB?",
  height = "50px",
  placeholder = "Enter a whole % value")
```

#### Recruitment 
Recent trends and how recruitment is accounted for in assessment 
```{r recruitment}
sd_question(
  type = "mc",
  id = "recruit_incl", 
  label = "Is recruitment modeled in the assessment?",
  options = c(
    "Yes" = "yes", 
    "No" = "no",
    "Unknown" = "unknown"
  )
)

sd_question(
  type = "textarea",
  id = "recruitment_model",
  label = "What is recruitment model used in the assessment?",
  height = "50px",
  placeholder = "i.e. Beverton-Holt")

sd_question(
  type = "textarea",
  id = "beg_recruit_yr",
  label = "What year does the recruitment time series begin?",
  height = "50px",
  placeholder = "Enter a year"
)
```

```{r other recruit}
sd_question(
  type = "textarea",
  id = "other_recruit_info",
  label = "Provide any additional recruitment information that should be considered. ",
  placeholder = "i.e. recent changes in recruitment, unavailable data streams, other options for empirical approaches, etc."
)
```

#### Assessment Type and Uncertainty 

```{r assessment}
sd_question("assessment_type")

sd_question(
  type = "textarea",
  id = "assessment_model",
  label = "What assessment model was used?",
  height = "50px",
  placeholder = "i.e. WHAM, ASAP, etc."
)

sd_question("terminal_assess_yr")
```

```{r retro}
sd_question("retro_pattern")

sd_question(
  type = "textarea",
  id = "retro_val",
  label = " What is the a retrospective pattern in the model?",
  height = "50px",
  placeholder = "Enter a value"
)

```

```{r data and uncertainty}
sd_question("data_used")
sd_question("missing_data")
sd_question("uncertainty_sources")
```

:::

<!-- --- additional_assessment_info -->
::: {.sd_page id=add_recruit_info}

##### Recruitment Estimates 
Report the most recent three years of recruitment estimates from the model

<!-- recruitment estimate options -->
::: {.columns}
::: {.column}
***Enter three years in the boxes below:***
```{r recruit years}
sd_question(
  type = "textarea",
  id = "recruit_year_est_1",
  label = "",
  height = "50px",
  placeholder = "Enter a year"
)

sd_question(
  type = "textarea",
  id = "recruit_year_est_2",
  label = "",
  height = "50px",
  placeholder = "Enter a year"
)

sd_question(
  type = "textarea",
  id = "recruit_year_est_3",
  label = "",
  height = "50px",
  placeholder = "Enter a year"
)
```

:::
::: {.column}
***Enter three estimates in the boxes below:***
```{r recruit ests}
sd_question("recruit_est_1")
sd_question("recruit_est_2")
sd_question("recruit_est_3")
```

:::
::: 
<!-- end columns -->

```{r}
# sd_nav()
```

:::

<!-- --- page_2 -->
::: {.sd_page id=climate_ecosystem}

### Climate and Ecosystem Questions

#### Climate vulnerability 
Use [Hare et al. 2016](https://journals.plos.org/plosone/article%3Fid=10.1371/journal.pone.0146756#sec027) to answer the following questions on climate vulnerability for this stock. 
```{r climate}
sd_question("climate_vulnerability")
sd_question("climate_direction")
```

#### Prey Habits
Use the [Prey Habits Shiny App](https://fishmaps.shinyapps.io/prey/) to answer the following questions:

```{r prey}
sd_question("prey_num")
sd_question("prey_info")
```

#### Fish Condition 
Use the most recent State of the Ecosystem reports to answer the following question:

```{r condition}
sd_question("fish_condition")

# sd_nav()
```

:::

<!-- --- page_3 -->
::: {.sd_page id=socioeconomic}

### Economic and Community Importance

Still being developed by the Risk Policy Working Group and the fishery performance report 

```{r other fish}
sd_question(
  type = "mc",
  id = "other_fish_quota", 
  label = "Does the fishery rely on quota of another species?",
  options = c(
    "Yes" = "yes", 
    "No" = "no"
    )
)

sd_question("other_quota_type")
```

:::

<!-- --- page_4 -->
::: {.sd_page id=additional}
### Additional Information

#### Reference Points

<!-- reference point estimates -->
::: {.columns}
::: {.column}
```{r ref pts types}

```

:::
::: {.column}

```{r ref vals}

```

:::
::: 
<!-- end columns -->


#### Specifications

```{r specs}
sd_question("ofl")
sd_question("abc")
sd_question("hcr")
sd_question("acct_measure")
```

#### Significant Catch 

```{r signif catch}
sd_question(
  type = "mc",
  id = "signif_catch_present", 
  label = "Is there siginificant catch of this stock in other fisheries *(i.e. greater than 5% utilization)*?",
  options = c(
    "Yes" = "yes", 
    "No" = "no"
  )
)

sd_question("signif_catch_info")
```

```{r}
# sd_nav()
```

:::

<!-- --- page_5 -->
::: {.sd_page id=end}
## End
You have completed the matrix. Please click below to exit the survey and download the report.

```{r redirect}
sd_redirect(id     = "redirect",
  url    = "https://nefmc-my.sharepoint.com/shared?listurl=https%3A%2F%2Fnefmc%2Esharepoint%2Ecom%2FGPDT%2FDocuments&viewid=81d11365%2D03a6%2D4333%2Dae66%2D18178ad0c83c&id=%2FGPDT%2FDocuments%2F250929%20Groundfish%20PDT%20Meeting%20by%20Webinar%2FRisk%20Policy%20Matrix%2FRisk%20Policy%20Matrix%5FAtlantic%20Wolffish%5FDRAFT%2Epdf&parent=%2FGPDT%2FDocuments%2F250929%20Groundfish%20PDT%20Meeting%20by%20Webinar%2FRisk%20Policy%20Matrix",
  label  = "Download the matrix report",
  button = TRUE,
  newtab = TRUE)
```

:::